---
title: "Final_Project"
author: "Evan Kurtz"
date: "2024-03-10"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
twitch <- read.csv("twitchdata-update.csv")
knitr::opts_chunk$set(echo = TRUE)
```

***1. Introduction***

My question is, what is the ratio of stream time to watch time? Basically, I want to know: how does the amount of time a streamer spends streaming affect how much time people spend watching them? A second interesting question is: how does the time spent streaming affect the amount of followers gained that year? In the end, how important is it that streamers spend much of their time streaming to be successful?**

My data was downloaded from Kaggle where it was uploaded by a user named Aayush Mishra. Mishra doesn't say, but I suspect the data was taken directly from Twitch.com itself. Each row is the name of a different streamer with there being 1000 in total. There are 11 columns in total: channel, watch time(minutes), streamtime(minutes), peak viewers, average viewers, followers, followers gained, views gained, partnered, mature, and language.**

***2. Data***

**Codebook**

**Channel:** the name of the Twitch streamer.

**Watch time(minutes):** the amount of minutes users have watched a particular streamer.

**Stream time(minutes):** the amount of minutes that a particular streamer was live.

**Peak viewers:** the maximum amount of viewers that a streamer had at one time in 2019.

**Average viewers:** the mean amount of viewers that a streamer had when live. 

**Followers:** the amount of followers a streamer had at the end of 2019.

**Followers gained:** the amount of followers that a streamer gained during 2019.

**Views gained:** the amount of views that a streamer gained in 2019. 

**Partnered:** whether a particular streamer is a Twitch partner. A program for highly successful streamers that gives them benefits for earning income from Twitch.

**Mature:** whether a Twitch streamer includes content for mature audiences or not according to their label. 

**Language:** the language that a Twitch streamer speaks on stream. 

```{r}
glimpse(twitch)
```

***3. Data analysis plan***

**A.** The outcome variables are the amount of time people spend watching (watch time) and the amount of followers that a streamer gains in a year. And the predictor variable is the amount of time a streamer spends live (stream time).

**B.** There are no comparison groups.


**C.** Data analysis.
```{r}
summary(twitch)

ggplot(data = twitch, mapping = aes(x = Stream.time.minutes.,y = Watch.time.Minutes.)) + 
  geom_point()
```

The summary statistics I printed out help to give me a broad overview of the averages, extremes, types, and amounts of data that I have. I have a better understanding of it now. 

The plot I made appears to not have a strong correlation between the amount of time streamed and the amount of time a streamer is watched, but I'll need to find exact numbers to know for sure. Perhaps, I will need to find a better variable to compare to the amount of time streamed in the end. 

**D.** I believe that creating a proportion of streamed minutes to watched minutes will be useful in seeing if the two are correlated. To get accurate data on whether stream time and watch time have a positive correlation, I may also need to remove the the upper extremes of the data to understand the more common trends. 


**E.** My hypothesis is that the more a streamer was live on Twitch, the more watch time they received from viewers. To know if this is true or not, I will need to find that there is a positive correlation between the two variables. The same applies to the question of whether stream time has a positive correlation with the number of followers gained in a year. 